---
format: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# iccbeta: Intraclass Correlation

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/iccbeta/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tmsalab/iccbeta/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


A function and vignettes for computing an intraclass correlation
described in Aguinis & Culpepper (in press). `iccbeta` quantifies the
share of variance in a dependent variable that is attributed to group
heterogeneity in slopes.

## Installation

You can install `iccbeta` from CRAN using:

```{r}
#| label: cran-installation
#| eval: false
install.packages("iccbeta")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r}
#| label: gh-installation
#| eval: false
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/iccbeta")
```

## Usage

To use the `iccbeta` package, load it into _R_ using:

```{r}
#| label: iccbeta-load-package
#| message: false
library("iccbeta")
```

From there, calling the `icc_beta()` function with either a `lmer()`
model object or the desired individual components will
compute the intraclass correlation:

```{r}
#| label: iccbeta-sample-call
#| eval: false
# Automatically calculate icc from model
results_model = icc_beta(<lmer-model>)

# Calculate icc from individual terms.
results_component = icc_beta(X, l2id, T, vy)
```

## Authors

Steven Andrew Culpepper and Herman Aguinis

## Citing the `iccbeta` package

To ensure future development of the package, please cite `iccbeta`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r}
#| label: iccbeta-citation
#| eval: false
citation("iccbeta")
```

## License

GPL (>= 2)